---
title: "formative.rmd"
author: "fengxian liu"
date: "2017/10/5"
output: html_document
---

```{r}
install.packages("dplyr")
```
Open a new markdown and install the needful package.

```{r}
setwd("/Users/FX/Desktop/Test 1 Fengxian Liu")
A1<-read.csv("HMXPC13_DI_v2_5-14-14.csv")
A1
```
Upload the MITx/Harvardx dataset to R as a dataframe named D1

```{r}
A2<-filter(A1,certified=="1")
A3<-dplyr::filter(A2, grepl('HarvardX/CS50x', course_id))
count(A3,certified)
```
How many people enrolled in HarvardX/CS50x recieved certification in 2012? 


```{r}
A4<-filter(A1,start_time_DI=="2012-10-15")  #people who registered on 2012/10/15
A5<-filter(A4,final_cc_cname_DI=="Columbia")   #people who are from Columbia and registered on 2012/10/15

count(A5)
count(A4)
```

How many people registered for HarvardX/CS50x from Columbia on October 15, 2012?


```{R}
A6<-filter(A1,final_cc_cname_DI=="Canada") #students from Canada
D2<-select(A6,start_time_DI,userid_DI)

```

Create a new data frame (D2) that includes student ID and registration date for all students from a country of your choice


```{r}
D3<-select(A1,start_time_DI,userid_DI)


```
Create a new data frame (D3) in which the column names are the registration dates, with one column containing the student ids and all other cells indicating a 1 if the student registered on that date or an NA if they did not



Now make the row names of D3 the student ids on your new data frame and remove the user id column from your data frame

Convert your data frame to a matrix (M1)

Create a new matrix which is the transposed version of your matrix (M2)

Create a third matrix (M3) that is a student by student matrix where the cells in the matrix represent if two studentes registered on the same day (This will take a lot of processing power, you may not be able to complete it if you have a large number of students)

Convert the diagonal of your matrix into NAs